% AMEL audit of LLM-judge benchmarks
% Working draft. Skeleton only; numbers and figures land after the pilot.
\documentclass[10pt,twocolumn]{article}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{microtype}
\usepackage[letterpaper,margin=0.75in,columnsep=0.35in]{geometry}
\usepackage{amsmath,amssymb}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage[numbers,sort&compress]{natbib}

\newcommand{\xspace}{}
\newcommand{\eg}{e.g.,\xspace}
\newcommand{\ie}{i.e.,\xspace}

\title{Conversation-history bias reshuffles LLM-judge benchmark rankings:\\
       an AMEL-driven audit of LLMBar and JudgeBench}

\author{
  Temkit Sid-Ali \\
  chut.app \\
  \texttt{sid@chut.app}
}

\begin{document}
\maketitle

\begin{abstract}
% Filled in after pilot + full audit.
TODO: one-paragraph abstract once pilot returns.
\end{abstract}

\section{Introduction}
\label{sec:intro}

\citet{temkit2026amel} documented \textit{AMEL}, a small but
consistent bias in LLM judges driven by accumulated conversation
history: when prior turns in the conversation share a verdict
polarity, the model's next verdict drifts in that direction. The
operational implication is that batched evaluation pipelines (one
conversation, many items) produce systematically different verdicts
than fresh-context evaluation (one conversation per item).

Most current LLM-judge benchmarks --- LLMBar
\citep{zeng2023llmbar}, MT-Bench, JudgeBench --- do not standardise
which administration regime is used. This paper asks whether that
choice changes which judge model wins.

TODO: contributions list once results are in.

\section{Related Work}
\label{sec:related}

TODO: AMEL, LLMBar, JudgeBench, B-score, Hankache et al. on
judge-bias audits.

\section{Methodology}
\label{sec:method}

TODO: benchmark choice, judge model panel, fresh vs batched
operationalisation, rank-shift metrics.

\section{Pilot}
\label{sec:pilot}

TODO: 1-week pilot on LLMBar Natural subset, 3 judges, decision
gate criteria, pilot results.

\section{Full Audit}
\label{sec:audit}

TODO: pending pilot pass.

\section{Discussion}

TODO.

\section{Limitations}

TODO.

\section{Conclusion}

TODO.

\section*{Reproducibility}
All code and data are available at
\url{https://github.com/chutapp/amel-llmbar-audit}. The
conversation-construction framework is vendored from
\texttt{chutapp/amel} (commit recorded in
\texttt{src/VENDORED\_FROM.md}) and re-used unchanged so that the
prior-conversation construction matches the original AMEL design.

\bibliographystyle{plainnat}
\bibliography{references}

\end{document}
